AFQ-Insight

### 2019-02-09 reports/manuscript/sections/introduction.tex
Adds a little bit more about multivariate analysis.

\item ROI-based selection, followed by multivariate analysis. Here, an ROI is
selected based on \emph{a priori} knowledge, and all the nodes or voxels in the
ROI are used together to fit a model that can predict differences between
individuals.

>>>>

\item ROI-based selection, followed by multivariate analysis. Here, an ROI is
selected based on \emph{a priori} knowledge, and all the nodes or voxels in the
ROI are used together to fit a model that can predict differences between
individuals. An example of that is the ``profilometry'' framework, in which
different diffusion metrics from a single tract are combined together to provide
input to a multivariate analysis of covariance, and linear discriminant analysis
\cite{dayan2016profilometry}. Other work has used random forests algorithms
applied to the corticospinal tract to discriminate between patients with ALS and
matched controls \cite{sarica2017corticospinal}
